Variational Monte Carlo on bosonic systems

### 2018-01-28 project_1/article/article.tex
Add explicit expression for the Laplacian

>>>>

            Using this we are now able to write the closed form expression of
            the Laplacian of the trial wavefunction.
                    %\nonumber \\
                    %&\qquad
                    2a
                    \sum_{m \neq k}^N
                    \Biggl[
                        \frac{1}{r_{km}^2(r_{km} - a)}
                        - \frac{r_{km} - 1}{r_{km}^2(r_{km} - a)^2}
                    \Biggr]
                    -4\alpha(x_k\vf{e}_i + y_k\vf{e}_j + \beta z_k\vf{e}_k)
                    \cdot
                    a\sum_{m \neq k}^N
                    \frac{\vf{r}_k - \vf{r}_m}{r_{km}^2(r_{km} - a)}
                    + \Biggl[
                        a\sum_{m \neq k}^N
                        \frac{\vf{r}_k - \vf{r}_m}{r_{km}^2(r_{km} - a)}
                    \Biggr]^2.
            To ease the load on the CPU we try to restrict the number of times
            we evaluate the sums. For brevity we introduce the following
            functions
                \xi_k(\vf{r}, a)
                &= \sum_{m \neq k}^N
                \Biggl[
                    \frac{1}{r_{km}^2(r_{km} - a)}
                    - \frac{r_{km} - 1}{r_{km}^2(r_{km} - a)^2}
                \Biggr] \\
                \sum_{m \neq k}^N
                \frac{1 - a}{r_{km}^2(r_{km} - a)^2}, \\
                \vfg{\zeta}_k(\vf{r}, a)
                \sum_{m \neq k}^N
                \frac{\vf{r}_k - \vf{r}_m}{r_{km}^2(r_{km} - a)}.
            We can then rewrite the expression for the Laplacian to
                    %\nonumber \\
                    %&\qquad
                    2a\xi_k(\vf{r}, a)
                    -4a\alpha(x_k\vf{e}_i + y_k\vf{e}_j + \beta z_k\vf{e}_k)
                    \cdot
                    \vfg{\zeta}_k(\vf{r}, a)
                    + a^2\vfg{\zeta}_k(\vf{r}, a)^2.
                Both $\xi_k$ and $\vfg{\zeta}_k$ can be evaluated in a common
                loop. Using this expression for the Laplacian we can find the
                local energy from
                    \frac{\bra{\vf{r}}H\ket{\Psi_T}}
                    =
                    \sum_{k}^N
                        -\frac{\hbar^2}{2m}
                        + V_{\text{ext}}(\vf{r})
                    \sum_{i < j}^N w(\vf{r}_i, \vf{r}_j).
